---
title: "Project 1"
author: "Prithviraj Kadiyala"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    csl: biomed-central.csl
    df_print: paged
    fig_caption: yes
    fig_height: 6
    fig_width: 7
    number_sections: yes
    theme: journal
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    df_print: kable
    fig_caption: yes
    fig_height: 6
    fig_width: 7
    highlight: tango
    toc: yes
    toc_depth: 4
#bibliography: project.bib
abstract: This project is all about analysing the SWDEFECTS file using R and probability theory. You will need to change the headings to reflect the nature of the project intentions. Re write this abstract as the last thing you do.
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction to the data

## Data and variables(see MS pg. 77,125)
Describe the data and the problem we wish to investigate.

## Summary Table 

Create the summary table (TABLE SIA3.2) found on page 125.

Using $\LaTeX$ construct the formulae for 

1. Accuracy
2. Detection rate
3. False alarm rate
4. Precision

Latex Example: See (http://www.stat.cmu.edu/~cshalizi/rmarkdown/#elements-of-math-mode)

$$
\begin{eqnarray}
P(|X-\mu| > k) & = & P(|X-\mu|^2 > k^2)\\
& \leq & \frac{\mathbb{E}\left[|X-\mu|^2\right]}{k^2}\\
& \leq & \frac{\mathrm{Var}[X]}{k^2}
\end{eqnarray}
$$

# R functions
Using the above definitions make R functions that will create the required probabilities, please remove `eval=FALSE` when creating the functions :

```{r accuracy}
acc=function(a,b,c,d)
{
  accuracy = (a+d)/(a+b+c+d)
  accuracy
}
```

```{r detection}
detect=function(b,d)
{
  detectionrate = d/(b+d)
  detectionrate
}
```

```{r alarm}
falarm=function(a,c)
{
  falsealarm = c/(a+c)
  falsealarm
}
```

```{r precision}
prec=function(c,d)
{
  precision=d/(c+d)
  precision
}
```


# Create the tables in Figure SIA3.1

The tables do not have to be formatted exactly as those in the book. Have the functions produce a suitable barplot also. 

As a guide and help -- see code below

```{r }
swd=read.csv("swdefects.csv")
head(swd)
tab=with(swd, table(predict.loc.50,defect))
barplot(tab, beside=TRUE, leg=TRUE)
tab2=addmargins(tab)
tab2
```

```{r maketable}
#Creates tables based on the column names given to it.
createtable=function(df,col1,col2){
  tab=with(swd, table(df[[col1]],df[[col2]]))
  barplot(tab, beside=TRUE, leg=TRUE, main=col1)
  tab2=addmargins(tab)
  tab2
}
# creating tables.
tabloc = createtable(swd,"predict.loc.50","defect")
tabloc
tabvg = createtable(swd,"predict.vg.10","defect")
tabvg
tabevg = createtable(swd,"predict.evg.14.5","defect")
tabevg
tabivg = createtable(swd,"predict.ivg.9.2","defect")
tabivg
```



# Create the table on page 127, TABLE SIA3.3

You must create a function that will do this. That is the table should be made by invocation of the function. You may write your own code from scratch -- make sure it is hash commented. Below is a help (remember: you can make the function as you wish) -- you can use the previously made functions in this function also.
More precisely the function must make:

>
  1. The Table
  2. A suitable barplot
  

  

```{r allmethods}
allmethods = function(df) # dataframe
{
  tabloc = createtable(swd,"predict.loc.50","defect")
  tabvg = createtable(swd,"predict.vg.10","defect")
  tabevg = createtable(swd,"predict.evg.14.5","defect")
  tabivg = createtable(swd,"predict.ivg.9.2","defect")
  
  probs=c("Accuracy","Detection Rate","False Alarm Rate", "Precision")
  mths = c("Lines of Code", "Cyclomatic complexity", "Essential complexity", "Design complexity")
  
  mat = matrix(NA, nrow = length(mths), ncol = length(probs), dimnames=list(mths,probs))
  for (i in 1:length(mths)) {
    if(i==1){
      a = tabloc[1,1]
      b = tabloc[1,2]
      c = tabloc[2,1]
      d = tabloc[2,2]
    }
    else if(i==2){
      a = tabvg[1,1]
      b = tabvg[1,2]
      c = tabvg[2,1]
      d = tabvg[2,2]
    }
    else if(i==3){
      a = tabevg[1,1]
      b = tabevg[1,2]
      c = tabevg[2,1]
      d = tabevg[2,2]
    }
    else{
      a = tabivg[1,1]
      b = tabivg[1,2]
      c = tabivg[2,1]
      d = tabivg[2,2]
    }
    #Calculate a,b,c,d here
    for (j in 1:length(probs)) {
      if(j==1){
        mat[i,j] = acc(a,b,c,d)
      }
      else if(j==2){
        mat[i,j] = detect(b,d)
      }
      else if(j==3){
        mat[i,j] = falarm(a,c)
      }
      else{
        mat[i,j] = prec(c,d)
      }
    }
  }
  mat
  
  
  as.table(mat)
}

tab=allmethods(df = swd)
tab
```
