---
title: 'Assignment 2'
author: "Prithviaj Kadiyala"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions{9/17}

## Q 1
###a P(Expert|Matched Prints)

$$
\begin{align}
P(Expert \, did \, not \, identify| Matched \,Prints)&=1-P(Expert\, Identify|Matched \,prints)\\
&=1-0.9212 \\
&= 0.0788 \\
&= 7.88\%
\end{align}
$$

###b P(Novice|Matched Prints)
$$
\begin{align}
P(Novice \, will \, not \, identify| Matched \,Prints)&=1-P(Novice\, Identify|Matched\, prints)\\
&=1-0.7455 \\
&= 0.2545 \\
&= 25.45\%
\end{align}
$$

###c 
Since, Novice has higher probability of failing to identifying the matched prints. It is possible that it will most likely be a novice that fails to identify the matched prints.

## Q 2

###a P(Positive|User)
$$
\begin{align}
P(+|User) = 0.5
\end{align}
$$

###b P(Negative|Non-User)
$$
\begin{align}
P(-|User_c) = 0.99
\end{align}
$$

###c P(User| Positive)
$$
\begin{align}
P(User|+) &= \frac{P(A \cap B)}{P(B)}\\
&=\frac{0.1*0.5}{(0.1*0.5)+(0.9*0.01)}\\
&=\frac{0.05}{0.059}\\
&= 0.8475\\
&= 85 \%
\end{align}
$$ 

## Q 3

```
Consider two sets n1 and n2 with the number of elements a1 and a2, respectively. The number of different samples that can be formed is a1*a2. If another set n3 (with the number of elements a3) is added, the number of different samples that can be formed becomes (a1*a2)*a3. It follows that for a set nk, the number of different samples that can be formed is a1*a2*.*ak, which is a1a2.ak.
```


## Q 4
```
Consider a set of N elements. If we want to choose n elements (without replacement) from N elements, the number of options for each element are N * (N - 1) * (N - 2) * (N - 3) * ... * (N - n + 1) This is the same as N!, until a certain point. Since we only want n elements, the point that N! stops is (N - n+1) so the formula above reduces to
```

$$\frac{N!}{(N-n)!}$$

## Q 5
By Theorem 3.2, the number of distinct ways to order N elements from a group of N elements is 

<center>
$\frac{N!}{(N-n)!}$
</center>

However, according to Theorem 3.1, the number of distinct ways to partition N elements from a group of N elements is also 

<center>
$(A)(n_1)!(n_2)!...(n_k)!$
</center>

Where A is the number of ways to partition N elements into k groups. So we have 

<center>
$N!=(A)(n_1)!(n_2)!....(n_k)!$
</center>

Solving for A gives 
<center>
$A=\frac{N!}{(n_1)!(n_2)!....(n_k)!}$
</center>


## Q 6

To sample n elements from a group of N elements, we can use the notation: $\binom{N}{n}$, which is N choose n. This is equivalent to partioning N elements into k=2 groups - the elements sampled and the elements not sampled. By Theorem 3.3, that results in

<center>
$$
\binom{N}{n} = \frac{N!}{n!(N-n)!}
$$
</center>

## Q 7
###a Sum of Probabilities
<center>
$$
\begin{align}
p(Y) &= P(0) + P(1) + P(2) + P(3) + P(4)\\
&=0.09+0.30+0.37+0.20+0.04\\
\end{align}
$$
</center>

```{r}
P = 0.09+0.30+0.37+0.20+0.04
P
```

###b $P(3 \cup 4)$
$P(3 \cup 4) = P(3) + P(4)$
```{r}
P = 0.20+0.04
P
```

###c $P(Y \leq 2)$
$P(Y \leq 2) = P(0) + P(1) + P(2)$
```{r}
P= 0.09+0.30+0.37
P
```

## Q 8
###a Property of Probability distribution
Property of Probability distribution of discrete variables is that P(Y)=1.

So,

$P(Y)= P(0) + P(1) + ... + P(20)$

```{r}
P=0.17+0.10+0.11+0.11+0.10+0.10+0.07+0.05+0.03+0.02+0.02+0.02+0.02+0.02+0.01+0.01+0.01+0.01+0.01+0.005+0.005
P
```

###b $P(Y \geq 10)$
$P(Y \geq 10)=1-\sum P(Y \leq 9)$
```{r}
P = 1-(0.17+0.10+0.11+0.11+0.10+0.10+0.07+0.05+0.03+0.02)
P
```

###c Mean and Variance
$Mean(\mu)=\sum_{0}^{20}y.P(y)$
```{r}
mean = (0*0.17)+(1*0.10)+(2*0.11)+(3*0.11)+(4*0.10)+(5*0.10)+(6*0.07)+(7*0.05)+(8*0.03)+(9*0.02)+(10*0.02)+(11*0.02)+(12*0.02)+(13*0.02)+(14*0.01)+(15*0.01)+(16*0.01)+(17*0.01)+(18*0.01)+(19*0.005)+(20*0.005)
mean
```

$Variance(\sigma^2) = \frac{1}{N}.\sum (x_i- \mu)^2$

```{r}
y=c(0.17,0.10,0.11,0.11,0.10,0.10,0.07,0.05,0.03,0.02,0.02,0.02,0.02,0.02,0.01,0.01,0.01,0.01,0.01,0.005,0.005)
```

```{r}
#Doing the summation part
for (i in 1:length(y)) {
    sum <- (y[i]-mean)^2
}
# we do 1/N now
sum=sum/21
sum
```

## Q 9
###a P(Y=10)
```{r}
x=rep(c(1,0),c(70,30))
dbinom(10,25,0.7)
```

###b $P(Y \leq 5)$
```{r}
pbinom(5,25,0.7)
```

###c Mean and Variance

$Mean = n*p$
```{r}
mean = 25*0.7
mean
```

$$
Variance(\sigma^2) = n*p*q\\
\sigma=\sqrt(npq)
$$
```{r}
variance=25*0.7*0.3
sqrt(variance)
```

###d Interpretation
The results indicate that the number of foreign students graduating with a Ph.D. in Engineering in a group of 25 will be, on average, `r mean`. Also, according to Chebyshev's, at least 75% of the samples will be within 2 standard deviations from
the mean or in the interval (`r round((mean - 2*sqrt(variance)),2)`, `r round((mean + 2*sqrt(variance)),2)`).

## Q 10
###a $P(Y=10)$
```{r}
dmultinom(1:10,prob=c(0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1))
```

## Q 11
###a Formula for Probability Distribution
$P(Y=y)=p*q^(y-1)$
```{r}
PD=0.4*0.6^(y-1)
```

###b What is E(Y)?
E(Y) is mean.

We can calculate mean using the formula $\mu=\frac{1}{p}$
```{r}
mean=1/0.4
mean
```

###c $P(Y=1)$
```{r}
PD=0.4*0.6^(1-1)
PD
```

###d $P(Y \geq 2)$
```{r}
dgeom(1, 0.4)
```















