---
title: 'Assignment 2'
author: "Prithviaj Kadiyala"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions{17/17}

## Q 1
###a P(Expert|Matched Prints)

$$
\begin{align}
P(Expert \, did \, not \, identify| Matched \,Prints)&=1-P(Expert\, Identify|Matched \,prints)\\
&=1-0.9212 \\
&= 0.0788 \\
&= 7.88\%
\end{align}
$$

###b P(Novice|Matched Prints)
$$
\begin{align}
P(Novice \, will \, not \, identify| Matched \,Prints)&=1-P(Novice\, Identify|Matched\, prints)\\
&=1-0.7455 \\
&= 0.2545 \\
&= 25.45\%
\end{align}
$$

###c 
Since, Novice has higher probability of failing to identifying the matched prints. It is possible that it will most likely be a novice that fails to identify the matched prints.

## Q 2

###a P(Positive|User)
$$
\begin{align}
P(+|User) = 0.5
\end{align}
$$

###b P(Negative|Non-User)
$$
\begin{align}
P(-|User_c) = 0.99
\end{align}
$$

###c P(User| Positive)
$$
\begin{align}
P(User|+) &= \frac{P(A \cap B)}{P(B)}\\
&=\frac{0.1*0.5}{(0.1*0.5)+(0.9*0.01)}\\
&=\frac{0.05}{0.059}\\
&= 0.8475\\
&= 85 \%
\end{align}
$$ 

## Q 3

```
Consider two sets n1 and n2 with the number of elements a1 and a2, respectively. The number of different samples that can be formed is a1*a2. If another set n3 (with the number of elements a3) is added, the number of different samples that can be formed becomes (a1*a2)*a3. It follows that for a set nk, the number of different samples that can be formed is a1*a2*.*ak, which is a1a2.ak.
```


## Q 4
```
Consider a set of N elements. If we want to choose n elements (without replacement) from N elements, the number of options for each element are N * (N - 1) * (N - 2) * (N - 3) * ... * (N - n + 1) This is the same as N!, until a certain point. Since we only want n elements, the point that N! stops is (N - n+1) so the formula above reduces to
```

$$\frac{N!}{(N-n)!}$$

## Q 5
By Theorem 3.2, the number of distinct ways to order N elements from a group of N elements is 

<center>
$\frac{N!}{(N-n)!}$
</center>

However, according to Theorem 3.1, the number of distinct ways to partition N elements from a group of N elements is also 

<center>
$(A)(n_1)!(n_2)!...(n_k)!$
</center>

Where A is the number of ways to partition N elements into k groups. So we have 

<center>
$N!=(A)(n_1)!(n_2)!....(n_k)!$
</center>

Solving for A gives 
<center>
$A=\frac{N!}{(n_1)!(n_2)!....(n_k)!}$
</center>


## Q 6

To sample n elements from a group of N elements, we can use the notation: $\binom{N}{n}$, which is N choose n. This is equivalent to partioning N elements into k=2 groups - the elements sampled and the elements not sampled. By Theorem 3.3, that results in

<center>
$$
\binom{N}{n} = \frac{N!}{n!(N-n)!}
$$
</center>

## Q 7
###a Sum of Probabilities
<center>
$$
\begin{align}
p(Y) &= P(0) + P(1) + P(2) + P(3) + P(4)\\
&=0.09+0.30+0.37+0.20+0.04\\
\end{align}
$$
</center>

```{r}
P = 0.09+0.30+0.37+0.20+0.04
P
```

###b $P(3 \cup 4)$
$P(3 \cup 4) = P(3) + P(4)$
```{r}
P = 0.20+0.04
P
```

###c $P(Y \leq 2)$
$P(Y \leq 2) = P(0) + P(1) + P(2)$
```{r}
P= 0.09+0.30+0.37
P
```

## Q 8
###a Property of Probability distribution
Property of Probability distribution of discrete variables is that P(Y)=1.

So,

$P(Y)= P(0) + P(1) + ... + P(20)$

```{r}
P=0.17+0.10+0.11+0.11+0.10+0.10+0.07+0.05+0.03+0.02+0.02+0.02+0.02+0.02+0.01+0.01+0.01+0.01+0.01+0.005+0.005
P
```

###b $P(Y \geq 10)$
$P(Y \geq 10)=1-\sum P(Y \leq 9)$
```{r}
P = 1-(0.17+0.10+0.11+0.11+0.10+0.10+0.07+0.05+0.03+0.02)
P
```

###c Mean and Variance
$Mean(\mu)=\sum_{0}^{20}y.P(y)$
```{r}
mean = (0*0.17)+(1*0.10)+(2*0.11)+(3*0.11)+(4*0.10)+(5*0.10)+(6*0.07)+(7*0.05)+(8*0.03)+(9*0.02)+(10*0.02)+(11*0.02)+(12*0.02)+(13*0.02)+(14*0.01)+(15*0.01)+(16*0.01)+(17*0.01)+(18*0.01)+(19*0.005)+(20*0.005)
mean
```

$Variance(\sigma^2) = \frac{1}{N}.\sum (x_i- \mu)^2$

```{r}
y=c(0.17,0.10,0.11,0.11,0.10,0.10,0.07,0.05,0.03,0.02,0.02,0.02,0.02,0.02,0.01,0.01,0.01,0.01,0.01,0.005,0.005)
```

```{r}
#Doing the summation part
for (i in 1:length(y)) {
    sum <- (y[i]-mean)^2
}
# we do 1/N now
sum=sum/21
sum
```

## Q 9
###a P(Y=10)
```{r}
x=rep(c(1,0),c(70,30))
dbinom(10,25,0.7)
```

###b $P(Y \leq 5)$
```{r}
pbinom(5,25,0.7)
```

###c Mean and Variance

$Mean = n*p$
```{r}
mean = 25*0.7
mean
```

$$
Variance(\sigma^2) = n*p*q\\
\sigma=\sqrt(npq)
$$
```{r}
variance=25*0.7*0.3
sqrt(variance)
```

###d Interpretation
The results indicate that the number of foreign students graduating with a Ph.D. in Engineering in a group of 25 will be, on average, `r mean`. Also, according to Chebyshev's, at least 75% of the samples will be within 2 standard deviations from
the mean or in the interval (`r round((mean - 2*sqrt(variance)),2)`, `r round((mean + 2*sqrt(variance)),2)`).

## Q 10
###a $P(Y=10)$
```{r}
dmultinom(c(5,5,5,5,5,5,5,5,5,5),prob=c(0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1))
```

###b $P(Y < 2)$

$P(Y<2)=P(y=0)+P(y=1)$
```{r}
ans=dbinom(0,50,0.1)+dbinom(1,50,0.1)
ans
```


## Q 11
###a Formula for Probability Distribution
$P(Y=y)=p*q^(y-1)$
```{r}
PD=0.4*0.6^(y-1)
```

###b What is E(Y)?
E(Y) is mean.

We can calculate mean using the formula $\mu=\frac{1}{p}$
```{r}
mean=1/0.4
mean
```

###c $P(Y=1)$

where k=y-1

```{r}
dgeom(0,prob=0.4)
```

###d $P(Y > 2)$

$P(Y > 2)=1-P(Y \leq 2)$
```{r}
ans = 1-(dgeom(0,0.4)+dgeom(1,0.4))
ans
```

## Q 12
###a
```{r}
dhyper(0:8,8,201,10)
```

This shows us that getting at leat 1 facility that treats hazardous waste on-site is `r dhyper(1,8,201,10)`. Similarly, getting more than 1 has reduced probability and getting all 8 of those is very very less. `r dhyper(8,8,201,10)`

###b
```{r}
dhyper(4,8,201,10)
```

4 out of 10 facilities selected will process hazardous waste on-site is `r dhyper(4,8,201,10)`

## Q 13
###a

Since variance and the ean are the same for Poisson Distribution V(Y) = E(Y) = 0.03

###b
The following are the conditions must follow the Poisson Distribution:


>
  1. The experiment consists of counting the number of times Y a particular event occurs during a given unit of time or in a given area.
  2. The probability that an event occurs in a given unit of time, area and volume is the same for the units
  3. The number of events that occur in one unit of time, area, or volume is independent of the number that in the other units.


###c $P(Y=0)$

$$
\begin{align}
p(y)&=\frac{\lambda^y*e^(-\lambda)}{y!}\\
&=\frac{0.03^0*e^(-0.03)}{0!}
\end{align}
$$


```{r}
dpois(0,0.03)
```

## Q 14
###a Find c
We have to find the value of c such that the given function is proper density function.
We get the value of c such that $\int\limits_{-\infty}^{\infty}f(y)dy=1$

$$
\begin{align}
\int\limits_{0}^{1}c\,(2-y)dy&=1\\
&\implies c \left|2y-\frac{y^2}{2}\right|_0^1\\
& \implies c \left[2-\frac{1}{2}\right]=1\\
& \implies c*\frac{3}{2}=1\\
& \implies c=\frac{2}{3}
\end{align}
$$

As a result, the proper density function of Y is as follows:
$$
f(y) =
  \begin{cases}
    \frac{2}{3}\,(2-y)       & \quad \text{if } 0 \le y \le 1\\
    0                        & \quad \text elsewhere
  \end{cases}
$$

###b Find the distribution function of Y
We have to find the distribution function of Y,

$$
\begin{align}
F(y)&=\int\limits_{-\infty}^{y}f(t)dt\\
&=\int\limits_{0}^{y}\frac{2}{3}(2-t)dt\\
&= \frac{2}{3} \left|2t-\frac{t^2}{2}\right|_0^y\\
&=\frac{2}{3} \left[2y-\frac{y^2}{2}\right]\\
\end{align}
$$

Therefore, the distribution function of Y is given by 
$$
f(y) =
  \begin{cases}
    0                                     & \quad \text{if } y \le 0\\
    \frac{2}{3}\,(2y-\frac{y^2}{2})       & \quad \text{if } 0 \le y \le 1\\
    0                                     & \quad \text elsewhere
  \end{cases}
$$

### Compute $F(0.4)$
$$
\begin{align}
F(0.4)&=P(Y \leq 0.4)\\
&=\frac{2}{3}\left(2*0.4-\frac{(0.4)^2}{2}\right)\\
\end{align}
$$
```{r}
ans = (2/3)*((2*0.4)-((0.4^2)/2))
ans
```

### Compute $P(.1 \leq Y \leq .6)$

$$
\begin{align}
P(0.1 \leq Y \leq 0.6)&=P(Y \leq 0.6)-P(Y \leq 0.1)\\
&=\frac{2}{3}\left(2*0.6-\frac{(0.6)^2}{2}\right)-\frac{2}{3}\left(2*0.1-\frac{(0.1)^2}{2}\right)\\
\end{align}
$$

```{r}
ans = ((2/3)*((2*0.6)-((0.6^2)/2)))-((2/3)*((2*0.1)-((0.1^2)/2)))
ans
```

## Q 15

Given the amount of time Y that a commuter train is late a continuous random vaiable with pdf is given by
$$
f(y) =
  \begin{cases}
    \frac{3}{500}\,(25-y^2)       & \quad \text if -5 <  y < 5\\
    0                        & \quad \text elsewhere
  \end{cases}
$$

###a Mean and Variance calculation
We find the mean and variance of the amount of time in minutes the train is late
$$
\begin{align}
E(Y)&=\int\limits_{-\infty}^{\infty}yf(y)dy\\
&=\int\limits_{-5}^{5}y \left(\frac{3}{500}(25-y^2)\right)dy\\
&=\left[-\frac{3}{2000}y^4+\frac{3}{40}y^3\right]_{-5}^5\\
&=0
\end{align}
$$

Now, we find $E(Y^2)$
$$
\begin{align}
E(Y)&=\int\limits_{-\infty}^{\infty}y^2f(y)dy\\
&=\int\limits_{-5}^{5}y^2 \left(\frac{3}{500}(25-y^2)\right)dy\\
&=\left[-\frac{3}{2000}y^5+\frac{3}{40}y^3\right]_{-5}^5\\
&=5
\end{align}
$$

variance 
$$
\begin{align}
\sigma^2&=E(Y^2)-\left[E(Y)\right]^2\\
&=5-0\\
&=5
\end{align}
$$

###b Mean and variance of train is late in hours
Let Z show the time in Hours.
So, Z can be $Z=\frac{Y}{60}$

Computing Mean
$$
\begin{align}
E(Y)&=E(\frac{Y}{60})\\
&=\frac{1}{60}* E(Y)\\
&=\frac{1}{60}*0 \\
&= 0
\end{align}
$$

Variance
$$
\begin{align}
Var(Z) &= Var(\frac{Y}{60})\\
&=\frac{1}{60^2}*Var(Y)\\
&=\frac{1}{60^2}*5\\
&=\frac{1}{720}\\
&= 0.00138

\end{align}
$$

###c Mean and variance of train is late in minutes
We find the mean and variance of the amount of time in seconds the train is late

So $W=60Y$

Mean
$$
\begin{align}
E(W)&=E(60 * Y)\\
&=60 * E(Y)\\
&=60*0\\
&= 0
\end{align}
$$

Variance
$$
\begin{align}
Var(W) &= Var(60*Y)\\
&= 60^2 * Var(Y)\\
&= 60^2 * 5\\
&= 18000
\end{align}
$$

## Q 16

Data Givrn 

$\mu = 50$
$\sigma^2 = 3.2$

###a $P(Y > 45)$
$P(Y > 45) = 1- P(Y \leq 45)$
```{r}
ans = 1 - pnorm(45,50,3.2)
ans
```

###b $P(Y < 55)$
```{r}
pnorm(55,50,3.2)
```

###c $P(51 < y < 52)$
```{r}
pnorm(52,50,3.2)-pnorm(51,50,3.2)
```

## Q 17
Given 
$\mu = 605$
$\sigma^2 = 185$

###a $P(500 < Y < 700)$
```{r}
pnorm(700,605,185)-pnorm(500,605,185)
```

###b $P(400 < Y < 500)$
```{r}
pnorm(500,605,185)-pnorm(400,605,185)
```

###c $P(Y < 850)$
```{r}
pnorm(850,605,185)
```

###d $P(Y > 1000)$
$P(Y > 1000) = 1- P(y \leq 1000)$
```{r}
ans = 1- pnorm(1000,605,185)
ans
```

###e Top 10% ratings
When only 10% cars exceed the ratings. It means that the rest of the cars sum upto 90% of the ratings. So we find the rating that the 90% of the cars fall in.


```{r}
qnorm(0.9,605,185)
```





























