---
title: "Lab 1"
author: "Prithviraj Kadiyala"
date: "August 22, 2018"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Tasks

##Task 1

```{r get working directory}
getwd()
```

##Task 2

```{r read CSV}
ddt=read.csv("DDT.csv")
head(ddt)
```

##Task 3
###Task 3.1 Qualitative Variables


>
    1. River
    2. Species
    
###Task 3.2 Quantitative variables

>
    1. Mile
    2. Length
    3. Weight
    4. DDT

###Task 3.3 Number of Species


>
    Number of Species = 3
    
###Task 3.4 Subset

```{r Subset with Weight and Species}
with(ddt, ddt[WEIGHT>800 & SPECIES=="LMBASS",])
```

###Task 3.5 Subset River
```{r Subset with River and DDT}
with(ddt, ddt[DDT>4.0 & RIVER=="SCM",])
```

##Clicker Questions
###Q1
```{r}
summary(ddt$LENGTH)
```



>
    Mean length of Fish = 42.81 
    
###Q2
```{r Standard Deviation of Weight}
sd(ddt$WEIGHT)
```


>
    Standard Deviation of weight = 376.5461
    
###Q3
```{r}
plot(ddt$WEIGHT,ddt$LENGTH,xlab="WEIGHT",ylab="LENGTH")
```


>
    This is not the graph that is asked for the question.
    2 - No 

###Q4 Value of last v/20
```{r}
v=1:20
v/20
```

##Task 4
###Task 4.1
```{r Table of River}
table(ddt$RIVER)
```

###Task 4.2
```{r Color coded barplot of River}
sp=with(ddt,table(RIVER))
sp
barplot(sp, beside=TRUE, col=1:4)
```

###Task 4.3 table of River vs Fish
```{r Table of River vs Fish}
table(ddt$SPECIES,ddt$RIVER)
```

###Task 4.4 Barplot of River vs Species
```{r Barplot of River vs Species}
spriv=with(ddt,table(SPECIES,RIVER))
spriv
barplot(spriv,beside=TRUE,col=1:3)
```

##Task 5
###Task 5.1 Pie of Species
```{r Piechart of Species}
sp=with(ddt,table(ddt$SPECIES))
sp
pie(sp,col=1:3)
```


###Task 5.2 Pie of Rivers
```{r Piechart of Rivers}
sp=with(ddt,table(ddt$RIVER))
sp
pie(sp,col=1:4)
```

##Task 6
###Task 6.1 Boxplot DDT
```{r}
boxplot(ddt$DDT,col="Orange",data=ddt)
```

###Task 6.2 Boxplot Weight
```{r}
boxplot(ddt$WEIGHT,col="Red",data=ddt)
```

###Task 6.3 Boxplot Length
```{r}
boxplot(ddt$LENGTH,col="Red",data=ddt)
```

##Task 7 Coplots
###Task 7.1 colpot Weight vs Length when River is given
```{r WEIGHT VS LENGTH when RIVER is given}
rivcol=with(ddt, ifelse(RIVER=="FCM","Blue",
                        ifelse(RIVER=="LCM","Black",
                               ifelse(RIVER=="SCM","Green","Orange"))))
coplot(LENGTH~WEIGHT|RIVER,data=ddt,col=rivcol)
```

###Task 7.2 Coplot when DDT vs WEIGHT when Species is given
```{r DDt vs WEIGHT when SPECIES is gIVEN}
rivcol=with(ddt, ifelse(RIVER=="FCM","Red",
                        ifelse(RIVER=="LCM","Blue",
                               ifelse(RIVER=="SCM","Green","Orange"))))
coplot(DDT~WEIGHT|SPECIES,data=ddt,col=rivcol)
```

##Task 8
### Task 8.1 Box plot
```{r}
library(ggplot2)
p10 = qplot(RIVER,WEIGHT,data=ddt,fill=SPECIES,geom="boxplot")
p10 + labs(title = "Prithviraj Kadiyala")
```

### Task 8.2 Violin Plots
```{r}
p11 = qplot(RIVER,LENGTH,fill=SPECIES,data=ddt,geom="violin")
p11 + labs(title="Prithviraj Kadiyala")

```

### Task 8.3 Scatter Plot
```{r}
p12 = qplot(WEIGHT,LENGTH,col=SPECIES,data=ddt,geom="point")
p12 + labs(title="Prithviraj Kadiyala")
