---
title: "Lab 4"
author: "Prithviraj Kadiyala"
date: "September 10, 2018"
output:
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Task 1
```{r}
getwd()
```

#Task 2
```{r}
dird="C:\\Users\\prith\\OneDrive\\Documents\\MATH4753_FA18\\DATAxls\\"

myread=function(csv){
  fl=paste(dird,csv,sep="")
  read.table(fl,header=TRUE,sep=",")
}

spruce.df=myread("SPRUCE.csv")#MS pg478
with(spruce.df, dput(list(D=BHDiameter,H=Height), 
                     file="spruce.dat"))

#Last six lines
tail(spruce.df)
```

#Task 3
##Task 3.1 Trendscatter
```{r}
library(s20x)

trendscatter(Height~BHDiameter,f=0.5,data=spruce.df)
```

##Task 3.2 Linear Model Spruce.lm
```{r}
spruce.lm=lm(Height~BHDiameter,data=spruce.df)
summary(spruce.lm)
```

##Task 3.3 height.res and height.fit
```{r}
#residuals  created from the linear model object
height.res=residuals(spruce.lm)

#fitted values made from the linear model object
height.fit=fitted(spruce.lm)
```

##Task 3.4 Plot and Trendscatter plot
```{r}
#Make the plot using the plot function 
plot(height.fit,height.res, xlab="Fitted", ylab="Residuals")

# Put a lowess smoother through res vs fitted
trendscatter( height.fit,height.res, xlab="Fitted", ylab="Residuals")
```

```
The plot with Residuals and Fitted shows us a Quadractic graph while the plot earlier shows a gradually rising graph and flat towards the end.

```

##Task 3.5 plot Residuals
```{r}
# Quick way to make a residual plot
plot(spruce.lm, which =1)
```

##Task 3.6 Check Normality
```{r}
# Two plots testing normality
normcheck(spruce.lm,shapiro.wilk = TRUE)
```

```
P-Value = 0.29

Since the value is smaller, there is  higher evidence towards the Null hypothesis. But not high enough to disregard the hypothesis.
```

##Task 3.7 Conclusion
```
Applying the straight line to this data set is valid because the mode of the residual bar graph is 0 which means that there is no residual because the theoretical and actual were the same.
```

#Task 4
##Task 4.1 create quad.lm
```{r}
# Creating Quad.lm Linear model for quadratic equation
quad.lm=lm(Height~BHDiameter + I(BHDiameter^2),data=spruce.df)
summary(quad.lm)
```

##Task 4.2 Plot with Quadratic curve
```{r}
#add to the scatter plot
plot(Height~BHDiameter,bg="Blue",pch=21,cex=1.2,
ylim=c(0,max(Height)),xlim=c(0,max(BHDiameter)), 
main="Spruce height prediction",data=spruce.df)

myplot=function(x){
 0.86089580 +1.46959217*x  -0.02745726*x^2
 }
 
 #Or more general method
myplot=function(x){
 quad.lm$coef[1] +quad.lm$coef[2]*x  + quad.lm$coef[3]*x^2
 } 
 
curve(myplot, lwd=2, col="green3",add=TRUE)
```

##Task 4.3 Fitted Quadratic
```{r}
# Make quad.fit, a vector of fitted values
quad.fit = fitted(quad.lm) 

# Find the residuals for quadratic fit 
height.res_2 = residuals(quad.lm)

# Plot the residuals vs fitted values.
plot(height.res_2~quad.fit,bg="Blue",pch=21, cex=1.2,
     ylim=c(0,1.1*max(height.res_2)),xlim=c(0,1.1*max(quad.fit)),
     main="Residuals vs Fitted", ylab="Residuals", xlab="Fitted values")
```

##Task 4.4 Normcheck
```{r}

# construct QQ plot 
normcheck(quad.lm,shapiro.wilk = TRUE)
```

P-Value is 0.684.

This value is very much greater than the linear model making its case against Null hypothesis.

#Task 5
##Summarize Quad.lm
```{r}
#summarize quad.lm
summary(quad.lm)
```

The value of $\hat\beta_0$ = 0.8609

The value of $\hat\beta_1$ = 1.4696

The value of $\hat\beta_2$ = -0.0274


##Interval Estimates
```{r}
#Make interval estimates
ciReg(quad.lm)
```

##Height Prediction
```{r}
#predict height of spruce tree with quad.lm when diamater is 15,18 and 20cm
predict(quad.lm, data.frame(BHDiameter=c(15,18,20)))

# prediction using linear model spruce.lm when diameter is 15,18 and 20cm
predict(spruce.lm, data.frame(BHDiameter = c(15,18,20)))
```


##Multiple R-squared comparison

Multiple R-squared value for Quadratic model is 0.7741

Multiple R-squared value for Linear model is 0.6569

Multiple R-squared gives us the measure of variability.

**The Quadratic model is better here because it has more variability.**

**Quadratic model has more variability compared to linear model. We can say this by looking at multiple r-squared values above**


##Anova Comparison
```{r}
anova(spruce.lm,quad.lm)
```

##Calculate TSS, MSS and RSS
```{r}
height.qfit=fitted(quad.lm)
height.qfit

#  RSS=residual sum of squares
RSS=with(spruce.df,sum((Height-height.qfit)^2))
RSS

# MSS=model sum of squares
MSS=with(spruce.df,sum((height.qfit-mean(Height))^2))
MSS

# TSS=total sum of squares
TSS=with(spruce.df,sum((Height-mean(Height))^2))
TSS 

# Calculate MSS/TSS, and interpret it!
MSS/TSS
```

#Task 6
##Cooks plot
```{r}
cooks20x(quad.lm)
```

We can say that cooks distance is used to find the outliers in observations for predictor variables. It also gives the influence of all the observations on a fitted response values. If the observation using cooks distance is greater than thrice of the mean cooks distance might be an outlier.

##Highest cooks value removed
```{r}
quad2.lm=lm(Height~BHDiameter + I(BHDiameter^2) , data=spruce.df[-24,])
summary(quad2.lm)
summary(quad.lm)
```


We can conclude that quad2.lm which has highest cooks datum removed gives a better estimate when compared to quad.lm

When the cooks distance highest datum is removed from the data frame, the estimates will be improved.

#Bonus Question
```{r}
#add to the scatter plot
plot(Height~BHDiameter,bg="Blue",pch=21,cex=1.2,
ylim=c(0,max(Height)),xlim=c(0,max(BHDiameter)), 
main="Spruce height prediction",data=spruce.df)

myplot=function(x){
 result = 0.86089580 +1.46959217*x  -0.02745726*x^2
 result
 return (result)
 }
 
#For segments
myplot2=function(){
  n = 36
  mat <- matrix(ncol=1, nrow=n)
  for (x in 1:n){
    mat[x] = quad.lm$coef[1] +quad.lm$coef[2]*(spruce.df$BHDiameter[x])  + quad.lm$coef[3]*(spruce.df$BHDiameter[x])^2
  }
  return(mat)
} 
curveplot = myplot2()
curve(myplot, lwd=2, col="green3",add=TRUE)
with(spruce.df,{segments(BHDiameter,Height,BHDiameter,curveplot)})
with(spruce.df,arrows(5, 17.3, 11.4, 17.3))
with(spruce.df,text(5,18,"Highest Cook's distance",col="blue"))
```













